Macro drop and droplet profile detection during PGMAW process by image processing

### 2011-02-15 articles/MIG/paper-drop_v1.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\usepackage{graphicx}
\usepackage[sf]{subfigure}
\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

@@

\title[Macro drop and droplet profile detection during PGMAW process by image processing]{Macro drop and droplet profile detection during PGMAW process by image processing}

@@

\begin{abstract}

\end{abstract}

%Uncomment for PACS numbers title message
%\pacs{00.00, 20.00, 42.10}
% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
%\vspace{2pc}
%\noindent{\it Keywords}: Article preparation, IOP journals
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
% Comment out if separate title page not required
\maketitle

@@

A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arx Welding (PGMAW)
 process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
 In a PGMAW process, the weld quality is strongly related with the metal transfer  stability 
 (droplet deposition). The monitoring of metal transfer process
 will indicate the good deposition process \cite{WANG}. 
The macro drop kinetic measurement during static PGMAW process could improve the
understanding of some GMAW related phenomenon  \cite{CHO} as free surface 
fluctuations \cite{WANG}. The measurement of the geometry of the free surface 
of macrodrop or droplets is an important information for the understanding and
the validation of the simulation.

The monitoring of the shape and size of these welding objects uring
static PGMAW  is 
investigated with a 2D method. A shadowgraphy technique, or back lighting,
is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}.
 Due to the arc light interference and the relatively high 
speed of wire feed process, a high speed camera and an effective image processing algorithms are 
required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
per second \cite{WANG}. Therefore the algorithms have to be able to extract 
the geometrical information (area, size and others) from the macro drop and droplets,
from a huge amount of data. In addition, the voltage and current signals are directly related 
with the droplet formation at the wire \cite{BALSAMO}.

There have been many studies on visual sensing techniques for observing weld pool 
image \cite{BAE} and metal transfer process during welding \cite{LIN}.
Optical sensors like high speed  cameras and lighting systems have been
widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
Nevertheless the strong interference from the arc lightning required more than standard 
image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
analysis in weld pools or droplets \cite{WU1}.
Parameters such as macro drop or droplets surface, volumes 
or height has been measured using different and 
specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
\cite{NORDBRUCH}. However, to date, effective automatic image processing
of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

To perform geometrical analysis in macrodrop and droplet,
 a multipurpose C++  library (erCv) was developed at the lab. 
These library results from selected functions  from highly reliable 
open source libraries to images treatment, geometrical 
analysis, graph theory applications and image visualization.
In a first step, and despite the different static and dynamic weld conditions, 
as well as different current regime. A reliable 2D profiles and geometrical
parameters from macro drop and droplets, has been obtained using the mentioned library.
 Using this, a dimension and dimensionless analysis will 
be done. The intention is to help to simplify future numerical models and enhance monitoring by direct observation.

The paper is organized as follows. First, the experimental setup that will allow to appreciate the performance of the algorithm,
 to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
during welding process. Then 
 The library and the algorithms are explained and some results are shown on the macro drop and droplet study.

@@

The objective is to perform geometrical analysis and measure characteristic
times of the macro drop growth and the droplet during the free flight 
during  a static PGMAW process. 
A specific data acquisition setup was done at the lab in order to
synchronize all kind of signals and images versus time and space \cite{ChapuisThesis}.
The experimental setup is composed of a welding generator, a XY table, a data acquisition
system and a high speed camera as shown on figure \ref{schema-montage-experimental-GMAW}.
In this article only details on image acquisition setup and treatment will be outlined.

@@

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{images/schema-montage-experimental-GMAW.png}
\caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
\label{schema-montage-experimental-GMAW}
\end{center}
\end{figure}

@@

To the droplet or metal transfer drop the geometrical parameters to identify are:
The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
Finally in order to better understand the droplet dynamic \cite{}, 
the physical elements to identify are: the fall time $t_{a}$ and the average 
speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).

@@

As mentioned, a multipurpose image processing library was developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such: Macro drop, droplets and weld pool.
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
and portable library able to perform real time
 contour detection. erCv is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
erCv is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments to noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparators, watershed transformation,
 filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closer condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

@@

\subsection{ The Analyze methods}
\label{ the-analyze-methods}
\subsubsection{ Image Calibration}

@@

The idea is to extract the macro drop and droplet shapes 
from the raw images and therefore to extract the geometrical information.
 The most common approach is to segment the image \cite{WANG}. 
That means to separate in two fields (color) the image. The macro drop and droplet in one color and
the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition
 (shadowgraphy) the images are already segmented between
light and shadow zones (see figures \ref{photo-macro-drop-original});
 where the shadows zones are the projection of the macro drop and droplet.

However objects within the image under the arc may differ only by few intensity light level
from the background. In these images areas a contrast enhancement is necessary. 
Objects outside the arc, as the some regions of the macro drop profile,
 are clearly visible against the background. In these regions a contrast enhancement 
can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
 Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.

@@

Then, a regions adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolates patters (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max(value)$ is the grey level value choose to identify the pixels above
threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
 before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).

@@

Finally an impulse response filter to grey level gradient (Canny) is applied to extract 
the principal edges at image. In a binary image, all edges are principals,
therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
Nevertheless to guarantee a full detection of droplet and 
 macro drop profile, the canny parameters are adjusted to maximum, 
which means maximum edge detection sensibility.

@@

To the macro drop profile a user interaction algorithm is responsible
 to extract the continuous cord (white pixels) corresponding
 to the profile into a list. Note  that the macro drop and 
the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}.
 The substrate shadow projection is always the same if the optical
 path doesn’t change. Therefore the users have only to choose, to
 first image in the experience series, one extreme  of the cord 
corresponding to substrate profile (see figures \ref{photo-results-macro-drop}).
 Then the algorithm finds all new white pixels inside small neighbor around
 the pixels selected by the user. Each new white pixel  is added to the
 profile list. Starting at each new pixel, this process continues,
 automatically, until the other extreme of the cord, until the last
 image of the series.

@@

Give $S$ the set of points in the space image. The segments could 
be built between wherever two points of $S$. However, to fulfill
 the cords with segments, only the points placed together could define
 a segment. To choose the correct points of $S$ a Delaunay triangulation
 is made over $S$ \cite{CGAL}. Each point of $S$ is a vertice 
of a triangle and then each potential segment is a side of a triangle. 
The Delaunay triangulations guarantee a unique solution with minimal
 internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
 Give $\beta$ the cord surrounding the external hull of the Delaunay
 triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
 or square radius of a test circle, to travel from outside $\beta$ to inside
 the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
$n$ the number of triangles sides of triangulation
and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
with $i \in\{1,n\}$, a segment is build between the respective vertices or
 points. At the end of the process, a  set of segments knows as $\alpha$-shape has been created.
  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
 is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
 every side in the triangulation,  then no segment is created and $\alpha$-shape
 became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
 is sufficient to create a segment set around the droplet
 (see figure \ref{photo-droplet-alpha-shape}).

@@

Now it is possible to determine the geometrical parameters shown 
at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
are taken from the processed macro drop extracted profiles.
A loop algorithm applies this method to all frames at the experience to compute the wetting 
angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.

@@

\section{ Results}
In this part some results, performance and reliability of the library for a set of experiment
are shown. The basic experiment is a static PGMAW.
A macrodrop is feed by droplets that are assumed to flight vertically and
then feed the macrodrop. The macrodrop grows with a geometry that depends on the effects of gravity,
surface tension, heat transfert,...

@@

The algoritms are tested on a i7 processor from Intel with 1.87Ghz.

@@

The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
Macrodrop oscillations induced  wetting angle oscillations. Depending of the main oscillations during
a period, the local angle oscillation is more or less important. For pure Argon
gas, the equilibrium angle (60 degrees) rapidly reached and stays constant all along the welding.
For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.

\subsubsection{Discussion}
The noise in the measure for the basis could be attributed
to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.

@@

The modification of gas influences surface tension but also modifies the energy transfert from the plasma
to the workpiece. Even with same welding parameters, 
the difference of gas will modify the current lines distribution but also the arc length.
Nevertheless, the evolution of the basis and the  shape 
(figure \ref{fig::comp_gazs}) for the two gases are almost the same (figure \ref{fig::macrodrop}).
 This means that at first order the two evolutions
are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
Pure Argon shielding lead to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
at the triple joint (liquid-gas-substrate) is higher modifying then the behaviour of the overall interface.

@@

Despite the two dimensional analysis, the result gives important informations for 
simulation of metal transfert process. If  the droplet is assumed to be a sphere
 the kinetic energy of the droplet just before impact could be estimated. For our case,
The radius of the droplet is estimated at 0.56mm and the kinetic energy is around 6e-8J.

@@

\bibliography{paper_bain}

%\section*{References}
%\begin{thebibliography}{10}
%\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
%(Reading, MA: Addison-Wesley)
%\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
%\end{thebibliography}
\bibitem{CGAL} http://www.cgal.org 
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\usepackage{graphicx}
\usepackage[sf]{subfigure}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

@@

\title[Macro drop and droplet profile detection during PGMAW process by image processing]
{Macro drop and droplet profile detection during PGMAW process by image processing}

@@

\begin{abstract}
The paper describes some new image treatment algorithm used to 
detect profiles during arc welding process. The new algorithm 
are an agregation of some available algorithm of image treatement,
computational geometry and graph theory. The algorithm allows to extract precise
geometrical entities as closed or open profiles that could be used for monitoring
of welding process. The algorithm even if used external libraries is really efficient
and could be used for real time monitoring.
\end{abstract}

%Uncomment for PACS numbers title message
%\pacs{00.00, 20.00, 42.10}
% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
%\vspace{2pc}
\noindent{\it Keywords}: Arc welding, Image treatment, Melt pool,  Profile detection, Monitoring, 
% Uncomment for Submitted to journal title message
\submitto{\MST}
% Comment out if separate title page not required
\maketitle

@@

A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arc Welding (PGMAW)
 process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
 In a PGMAW process, the weld quality is strongly related with the metal transfer  stability 
 (droplet deposition). The monitoring of metal transfer process
 will indicate the good deposition process \cite{WANG}. 
The macro drop kinetic measurement during static PGMAW process could improve the
understanding of some GMAW related phenomenon  \cite{CHO} as free surface 
fluctuations \cite{WANG}. The measurement of the geometry of the free surface 
of macrodrop or droplets is an important information for the understanding of the physical phenomenom 
during welding and
the validation of the simulation of welding process.

In this article, the monitoring of the shape and size of these welding objects during
static PGMAW  is 
investigated with a 2D method. A shadowgraphy technique, or back lighting,
is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}.
 Due to the arc light interference and the relatively high 
speed of wire feed process, a high speed camera and an effective image processing algorithms are 
required \cite{WANG}. The  frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
per second. Therefore the algorithms have to be able to extract 
the geometrical information (area, size and others) from the macro drop and droplets,
from a huge amount of data. In addition, the voltage and current signals are directly related 
with the droplet formation at the wire \cite{BALSAMO}.

There have been many studies on visual sensing techniques for observing weld pool 
image \cite{BAE} and metal transfer process during welding \cite{LIN}.
Optical sensors like high speed  cameras and lighting systems have been
widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
Nevertheless the strong interference from the arc lightning required more than standard 
image treatment to analyse the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
analysis in weld pools or droplets \cite{WU1}.
Parameters such as macro drop or droplets surface, volumes 
or height has been measured using different and 
specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
\cite{NORDBRUCH}. However, to date, effective automatic image processing
of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

To perform geometrical analysis in macrodrop and droplet,
 a multipurpose C++  library (erCv) was developed at the lab. 
These library results from selected functions  from highly reliable 
open source libraries to images treatment, geometrical 
analysis, graph theory applications and image visualization.
In a first step, and despite the different static and dynamic weld conditions, 
as well as different current regime. A reliable 2D profiles and geometrical
parameters from macro drop and droplets, has been obtained using the mentioned library.
  The purpose is to help simplification of future numerical models and enhance monitoring by direct observation.

The paper is organized as follows. First, the experimental setup that will allow to appreciate the performance of the algorithm,
 to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
during welding process. 
Then The library and the algorithms are explained and some results are shown on the macro drop and droplet study.
The objective  is to perform geometrical analysis and measure characteristic
times of the macro drop growth and the droplet during the free flight 
during  a static PGMAW process.

@@

A specific data acquisition setup was done at the lab in order to
synchronize all kind of signals and images versus time and space \cite{ChapuisThesis}.
The experimental setup is composed of a welding generator, a XY table, a data acquisition
system and a high speed camera as shown on figure \ref{schema-montage-experimental-GMAW}.
In this article only details on image acquisition setup and treatment will be outlined.

@@

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{images/setup.png}
\caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
\label{schema-montage-experimental-GMAW}
\end{center}
\end{figure}

@@

For the droplet or metal transfer drop, the geometrical parameters to identify are:
The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
Finally in order to better understand the droplet dynamic \cite{}, 
the physical elements to identify are: the fall time $t_{a}$ and the average 
speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).

@@

As mentioned, a multipurpose image processing library was developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such as Macro drop, droplets and weld pool.
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
and portable library able to perform real time
 contour detection. The library is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
The library is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments to noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparators, watershed transformation,
 filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closer condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

@@

\subsection{ The Analyzing methods}
\label{ the-analyze-methods}
\subsubsection{ Image Calibration}

@@

The idea is to extract the macro drop and droplet shapes 
from the raw images and therefore to extract the geometrical information.
 The most common approach is to segment the image \cite{WANG}. 
That means to separate in two fields (color) the image. The macro drop and droplet in one color and
the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition
 (shadowgraphy) the images are already segmented between
light and shadow zones (see figures \ref{photo-macro-drop-original});
 where the shadow zones are the projection of the macro drop and droplet.

However objects within the image under the arc may differ only by few intensity light level
from the background. In these images areas, a contrast enhancement is necessary. 
Objects outside the arc, as  some regions of the macro drop profile,
 are clearly visible against the background. In these regions a contrast enhancement 
can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
 Therefore the contrast enhancements, or threshold, have to be adapted per regions in the image.

@@

Then, a  adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolated patterns (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max(value)$ is the grey level value choose to identify the pixels above
threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
 before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).

@@

Finally an impulse response filter to grey level gradient (Canny) is applied to extract 
the principal edges at image. In a binary image, all edges are principal,
therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
Nevertheless to guarantee a full detection of droplet and 
 macro drop profile, the canny parameters are adjusted to maximum, 
which means maximum edge detection sensibility.

@@

To the macro drop profile a user interaction algorithm is responsible
 to extract the continuous cord (white pixels) corresponding
 to the profile into a list. Note  that the macro drop and 
the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}.
 The substrate shadow projection is always the same if the optical
 path doesn't change. Therefore the users have only to choose, the
 first image in the experience series, one extreme  of the cord 
corresponding to substrate profile (see figures \ref{photo-results-macro-drop}).
 Then the algorithm finds all new white pixels inside small neighbor around
 the pixels selected by the user. Each new white pixel  is added to the
 profile list. Starting at each new pixel, this process continues,
 automatically, until the other extreme of the cord, until the last
 image of the series.

@@

Give $S$ the set of points in the space image. The segments could 
be built between wherever two points of $S$. However, to fulfill
 the cords with segments, only the points placed together could define
 a segment. To choose the correct points of $S$ a Delaunay triangulation
 is made over $S$ \cite{CGAL}. Each point of $S$ is a vertex
of a triangle and then each potential segment is a edge of a triangle. 
The Delaunay triangulations guarantee a unique solution with minimal
 internal angles for each triangle, which means  minimal
 length sides to the triangles \cite{GEOMETRICAL}.
 Give $\beta$ the cord surrounding the external hull of the Delaunay
 triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
 or square radius of a test circle, to travel from outside $\beta$ to inside
 the triangulation. The circle has to go through the triangles sides without touching the vertices. Give 
$n$ the number of triangles sides of triangulation
and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
with $i \in\{1,n\}$, a segment is marked between the respective vertices or
 points. At the end of the process, a  set of segments knows as $\alpha$-shape has been created.
  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can't go inside $\beta$, then $\alpha$-shape
 is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
 every side in the triangulation,  then no segment is created and $\alpha$-shape
 became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
 is sufficient to create a segment set around the droplet
 (see figure \ref{photo-droplet-alpha-shape}).

@@

Now it is possible to determine the geometrical parameters shown 
at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
angle measure, linear regressions or least squares (parabolic, ellipse, circle) 
are taken from the processed macro drop extracted profiles.
A loop algorithm applies this method to all frames at the experience to compute the wetting 
angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.

@@

\section{ Results}
In this part some results, performance and reliability of the library for a set of experiments
are shown. The basic experiment is a static PGMAW.
A macrodrop is feed by droplets that are assumed to flight vertically and
then feed the macrodrop. The macrodrop grows with a geometry that depends on the effects of gravity,
surface tension, heat transfert,...

@@

The algoritms are tested on a i7 processor from Intel with 1.87Ghz RAM.

@@

The evolution curves are also noisy. Videos investigation shows that the macrodrop oscillates during welding. 
Macrodrop oscillations induced  wetting angle oscillations. Depending of the main oscillations during
a period, the local angle oscillation is more or less important. For pure Argon
gas, the equilibrium angle (60 degrees) is rapidly reached and stays constant all along the welding.
For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.

\subsubsection{Discussions}
The noise in the measure for the basis could be attributed
to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.

@@

The modification of gas influences surface tension but also modifies the energy transfert from the plasma
to the workpiece. Even with same welding parameters, 
the difference of gas will modify the current lines distribution but also the arc length.
Nevertheless, the evolution of the basis and the  shape 
(figure \ref{fig::comp_gazs}) for the two gases are almost the same (figure \ref{fig::macrodrop}).
 This means that at first order the two evolutions
are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
Pure Argon shielding leads to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
at the triple joint (liquid-gas-substrate) is higher modifying then the behaviour of the overall interface.

@@

Despite the two dimensional analysis, the result gives important informations for 
simulation of metal transfert process. If  the droplet is assumed to be a sphere
 the kinetic energy of the droplet just before impact could be estimated. For our case,
The radius of the droplet is estimated at 0.56mm. % and the kinetic energy is around 6e-8J.

@@

%\bibliography{paper_bain}

%\section*{References}
%\begin{thebibliography}{10}
%\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
%(Reading, MA: Addison-Wesley)
%\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')

% \cite{BALSAMO}
%\cite{WANG}
%\cite{CHO}
%\cite{LIN}
% \cite{ZHANG4}
%\cite{BAE}
%\cite{NORDBRUCH}
%\bibitem{CGAL} http://www.cgal.org 
%\cite{ChapuisThesis}
%\cite{WU1}
%\cite{SEED}
% \cite{COCQUEREZ}
% \cite{OPENCV}
% \cite{GEOMETRICAL}
%\end{thebibliography}
\end{document}
